---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# neartools

<!-- badges: start -->
<!-- badges: end -->

There are many repetitive works when doing data harmonization and keeping track of communication with researchers.     

The goal of creating this package is to practice the "don't repeat yourself" (DRY) principle, making the daily work more handy. 


# Functions

Currently, this package contains functions as follows:

* `sav_to_csv`: Convert all the SPSS data files (*.sav*) to csv files. This conversion is needed because the maelstrom harmonization package does not read *.sav* data. This function can prevent repetitive work of converting *.sav* to *.csv* one by one. \
More details please see description in  `?sav_to_csv()`

* `pretty_template`: Automatically create an 'rmd' folder, create & open an rmd file with a nice looking template. This facilitates the communication with researchers & tracking the records. By default it complies an *html* file. \
More details please see description in  `?pretty_template()`. \
For more information about R markdown please see [here](https://rmarkdown.rstudio.com).

* *To be continued....*

## Installation

You can install the development version of neartools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Bolin-Wu/neartools")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(neartools)

# check function's documentation
?sav_to_csv()
?pretty_template()

## code usage
sav_to_csv("original_data", "SNAC-K")
pretty_template(name = "Reply to Prof XXX")
```
